### 2020-02-11 README.Rmd
Try to clean up README figure files

---
output:
  md_document:
    variant: gfm
---

@@

In functions throughout the `hurricaneexposure` package, storms are identified based on their name and year (e.g., Hurricane Floyd in 1999 is identified as "Floyd-1999"). Note that a few storms satisfied the criteria to be included in the data but were unnamed (e.g., "Notnamed" in 1991, "Subtrop" in 1997, etc.). These storms are identified in functions in the `hurricaneexposure` package based on the identifying name listed in the above table (e.g., "Notnamed-1991", "Td08-2016"), although for some research projects you may want to consider excluding these unnamed storms from the analysis.

>>>>

---
output: github_document
---

@@

In functions throughout the `hurricaneexposure` package, storms are identified based on their name and year (e.g., Hurricane Floyd in 1999 is identified as "Floyd-1999"). Note that a few storms satisfied the criteria to be included in the data but were unnamed (e.g., "AL13" in 1988). These storms are identified in functions in the `hurricaneexposure` package based on the identifying name listed in the above table, which is based on the first four characters of the storm's US ATCF code for the storm. For some research projects, however, you may want to consider excluding these unnamed storms from the analysis.
